Contracts for unions and intersections are hard for Nickel

### 2021-04-27 paper.tex
Add note on intersections sneaking in

Unions are also useful for configurations:
\begin{itemize}
    \item To represent nullable values in JSON
    \item For plain enumerations. For, the enabled protocols of a data server
        would be either \lstinline+HTTP+, \lstinline+FTP+ or \lstinline+SFTP+.
    \item To support different representations for a field. A file path could be
        accepted either as one string of \lstinline+"/"+-separated strings, or
        as a list of strings.
\end{itemize}

@@

In the case of Nickel, there is no pre-existing untyped language that we have to
support, so we are freer of our choice. However, Nickel is a configuration
language, whose contracts and types system is intended to be expressive enough
to encode data schemas encountered in practice. Since these schemas do use
untagged unions, there is a strong incentive to support untagged unions at the
type level, or at least, at the contract level.

@@

Untagged union, together with the other existing features of the type system,
are sufficient to implement the encoding illustrated in Figure
\ref{fig:union-encoding}. For example, let us represent an algebraic data type
(written in ML syntax) to an imaginary Nickel union type:

@@

\subsection{Union and intersections}
{\color{red}Goals of the section

Explain why having unions probably unavoidably leads one to have intersection.\vspace{0.5cm}}

$$(A -> B) \cap (C -> D) \sim (A \cup C) -> (B \cup D)$$
$$(A \cup B) -> C \sim (A -> C) \cap (B -> C)$$

% TODO: lazyness + parallelisation

>>>>

Unions are also useful for configurations:
\begin{itemize}
    \item To represent nullable values in JSON.
    \item For plain enumerations. For example, the enabled protocols of a data server
        would be either \lstinline+HTTP+, \lstinline+FTP+ or \lstinline+SFTP+.
    \item To support different representations of the same data. A file path could be
        accepted either as one string of \lstinline+"/"+-separated strings, or
        as a list of strings.
\end{itemize}

@@

In the case of Nickel, there is no pre-existing untyped language that we have to
support, so we are freer of our choice. However, Nickel is a configuration
language, whose contracts and types system is intended to be expressive enough
to encode data schemas encountered in the wild. Since these schemas do use
untagged unions, there is a strong incentive to support untagged unions at the
type level, or at least, at the contract level.

@@

Untagged union, together with the other existing features of the type system,
are sufficient to implement the encoding illustrated in Figure
\ref{fig:union-encoding}. For example, let us represent an algebraic data type
(written in ML syntax) as an imaginary Nickel union type:

@@

\subsection{Union and intersections}
{\color{red}Goals of the section
Explain why having unions probably unavoidably leads one to have intersection.\vspace{0.5cm}}

While our original motivation is in supporting unions, the rest of the paper
explore complete systems featuring union and intersection types. One could
wonder if the difficulties could then be sidestepped by removing intesection out
of the equation. But

\begin{enumerate}
    \item Most of the encountered issues already appear with bare unions.
    \item Intersection being dual to unions, they are showing up in some way
        when unions are put in negative positions. For example, a contract for
        $(A \cup B) \to C$ in a system without intersections must be equivalent
        to the contract $(A \to C) \cap (B \to C)$
\end{enumerate}
